Psych 254 Replication Project Analysis

### 2016-06-24 analysis.Rmd
analysis

```{r}
project_plan_sheet <- gs_url("https://docs.google.com/spreadsheets/d/1KZw75xlypvtK0cDoOHqXfFd3HsrfJ4gbq8iEJ6LOa0Y") # Need lookup=T to initialize
project_plan_raw <- gs_read_csv(project_plan_sheet)
```

@@

temp_project_keys <- c("mkeil","smraposo","jreynolds","jmarias","ehermann") # Only do users we have data for currently
length(project_keys[[1]]) - length(temp_project_keys) # How many people missing

@@

# Run all respective R code - need loop because project_keys same variable name
rm("project_info") # In case var is saved
for(project_key in temp_project_keys) { # change from temp - test; project_key <- "smraposo"
  fp <- paste0("project_analyses/",project_key,".R")
  source(fp)
  #tryCatch(source(fp), error=function(e) {errors <- c(errors,paste0(project_key," has an error in .R file"),print(fp))}) 
  if(exists("project_info")) { # If has project_info dataframe
    all_project_info <- rbind.fill(all_project_info,project_info) # add to all data
    rm("project_info") # In case other file does not same
  } else {
    errors <- c(errors,paste0(project_key," is missing project_info"))
  }
}

>>>>

```{r}
project_plan_sheet <- gs_url("https://docs.google.com/spreadsheets/d/1KZw75xlypvtK0cDoOHqXfFd3HsrfJ4gbq8iEJ6LOa0Y", lookup = TRUE) # Need lookup=T to initialize
project_plan_raw <- gs_read_csv(project_plan_sheet)
```

@@

temp_project_keys <- c("smraposo","jreynolds","jmarias","ehermann", "mkeil") # Only do users we have data for currently
length(project_keys[[1]]) - length(temp_project_keys) # How many people missing

@@

# Run all respective R code - need loop because project_keys same variable name
rm("project_info") # In case var is saved
for(project_key in temp_project_keys) { # change from temp - test; project_key <- "smraposo"
  print(project_key)
  fp <- paste0("project_analyses/",project_key,".R")
  source(fp)
  #tryCatch(source(fp), error=function(e) {errors <- c(errors,paste0(project_key," has an error in .R file"),print(fp))}) 
  if(exists("project_info")) { # If has project_info dataframe
    all_project_info <- rbind.fill(all_project_info,project_info) # add to all data
    rm("project_info") # In case other file does not same
  } else {
    errors <- c(errors,paste0(project_key," is missing project_info"))
  }
}
